---
title: "Prenatal Pesticide Exposure and Brain Development"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: cosmo
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(readr)
library(patchwork)
library(gWQS)
library(here)
library(tibble)
library(tidytext)
library(htmltools)
library(janitor)
library(readxl)

merged_all <- read.csv(here::here("reports/merged_all.csv"))

# data preprocessing
df.complete <- merged_all[, c(
  "maternal_age_birth", "ethnicity", "sessumscore", "maternal_BMI_anc", "ICV.y",
  "log_DEP", "log_DETP", "log_DMP", "log_DMTP", "log_CINA6", "log_D24",
  "log_PBA", "log_PNP", "log_TCP", "log_TDCCA",
  "LeftHemisphereThickness", "RightHemisphereThickness", "MeanThickness",
  "LeftHemisphereArea", "RightHemisphereArea", "TotalArea"
)]

df.complete <- df.complete[complete.cases(df.complete), ]
nrow(df.complete)

#naming
Exposure.Names <- c(
  "log_DEP", "log_DETP", "log_DMP", "log_DMTP", "log_CINA6",
  "log_D24", "log_PBA", "log_PNP", "log_TCP", "log_TDCCA"
)

# remove 'log_' prefix from pesticide names for output
df.complete <- df.complete %>%
  rename_with(~ stringr::str_remove(.x, "^log_"), all_of(Exposure.Names))

# update exposure names to match renamed columns
Exposure.Names <- stringr::str_remove(Exposure.Names, "^log_")

results <- read_csv(here::here("reports", "LR_models_summary_edited.csv"))

# New labels for publication
new_labels <- c(
  "log_DEP" = "DEP", 
  "log_DETP" = "DETP", 
  "log_DMP" = "DMP", 
  "log_DMTP" = "DMTP", 
  "log_PNP" = "PNP",
  "log_PBA" = "PBA", 
  "log_TDCCA" = "TDCCA",
  "log_CINA6" = "CINA6", 
  "log_TCP" = "TCP",
  "log_D24" = "D24"
)

# Fixing title labels
mri_labels <- c(
  "LeftHemisphereThickness" = "Left Hemisphere Thickness",
  "LeftHemisphereArea" = "Left Hemisphere Area",
  "RightHemisphereThickness" = "Right Hemisphere Thickness",
  "RightHemisphereArea" = "Right Hemisphere Area",
  "MeanThickness" = "Mean Thickness",
  "TotalArea" = "Total Area"
)

# ordering the outcomes
mri_vars <- names(mri_labels)

# Create a clean plotting dataset with significance labels and ordered factors
results_plot <- results %>%
  mutate(
    sig = ifelse(p.value < 0.05, "Significant", "Not significant"),  # label significance
    pesticide = factor(pesticide, levels = names(new_labels)),      # consistent pesticide order
    outcome = factor(outcome, levels = mri_vars)                     # consistent outcome order
  )


# Define thickness and area outcomes
thickness_outcomes <- c(
  "LeftHemisphereThickness",
  "RightHemisphereThickness",
  "MeanThickness"
)

area_outcomes <- c(
  "LeftHemisphereArea",
  "RightHemisphereArea",
  "TotalArea"
)

# ---------------------------
# THICKNESS PLOT
# ---------------------------
thick_data <- results_plot %>%
  filter(outcome %in% thickness_outcomes)

xlim_thick <- range(c(thick_data$conf.low, thick_data$conf.high), na.rm = TRUE)

p_thick2 <- ggplot(thick_data, aes(
  x = estimate, 
  y = pesticide, 
  color = sig,
  text = paste0(
    "Pesticide: ", as.character(pesticide),
    "<br>Effect Estimate (β): ", round(estimate, 2),
    "<br>95% CI: [", round(conf.low, 2), ", ", round(conf.high, 2), "]",
    "<br>p-value: ", signif(p.value, 2)
  )
)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40") +
  scale_color_manual(values = c("Significant" = "red", "Not significant" = "steelblue")) +
  scale_y_discrete(limits = rev(names(new_labels)), labels = new_labels) +
  facet_wrap(~ outcome, ncol = 1, labeller = labeller(outcome = mri_labels)) +
  coord_cartesian(xlim = xlim_thick) +
  labs(
    x = "β Estimate and 95% CI",
    y = NULL
  ) +
  theme_minimal(base_size = 13) +
  theme(
    legend.position = "none",
    strip.text = element_text(size = 12),
    axis.text.y = element_text(size = 11),
    axis.text.x = element_text(size = 10),
    panel.spacing = unit(2, "lines")
  )+ theme(
    axis.text.y = element_text(size = 8),
    plot.margin = margin(5, 5, 5, 5)
  )


# ---------------------------
# AREA PLOT
# ---------------------------
area_data <- results_plot %>%
  filter(outcome %in% area_outcomes)

xlim_area <- range(c(area_data$conf.low, area_data$conf.high), na.rm = TRUE)

p_area2 <- ggplot(area_data, aes(
  x = estimate, 
  y = pesticide, 
  color = sig,
  text = paste0(
    "Pesticide: ", as.character(pesticide),
    "<br>Effect Estimate (β): ", round(estimate, 2),
    "<br>95% CI: [", round(conf.low, 2), ", ", round(conf.high, 2), "]",
    "<br>p-value: ", signif(p.value, 2)
  )
)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40") +
  scale_color_manual(values = c("Significant" = "red", "Not significant" = "steelblue")) +
  scale_y_discrete(limits = rev(names(new_labels)), labels = new_labels) +
  facet_wrap(~ outcome, ncol = 1, labeller = labeller(outcome = mri_labels)) +
  coord_cartesian(xlim = xlim_area) +
  labs(
    x = "β Estimate and 95% CI",
    y = NULL
  ) +
  theme_minimal(base_size = 13) +
  theme(
    legend.position = "none",
    strip.text = element_text(size = 12),
    axis.text.y = element_text(size = 11),
    axis.text.x = element_text(size = 10),
    panel.spacing = unit(2, "lines")
  )+ theme(
    axis.text.y = element_text(size = 8),
    plot.margin = margin(5, 5, 5, 5)
  )



#--------------------------------------
#WQS
#--------------------------------------
#loading in the wqs files
WQS.LHemThick <- readRDS(here::here("reports", "WQS_LHemThick.rds"))
WQS.RHemThick <- readRDS(here::here("reports", "WQS_RHemThick.rds"))
WQS.MeanThick <- readRDS(here::here("reports", "WQS_MeanThick.rds"))

WQS.LHemArea <- readRDS(here::here("reports", "WQS_LHemArea.rds"))
WQS.RHemArea <- readRDS(here::here("reports", "WQS_RHemArea.rds"))
WQS.TotalArea <- readRDS(here::here("reports", "WQS_TotalArea.rds"))



#function for wqs plots
plot_wqs_weights <- function(wqs_obj, model_name, exposures) {
  
  threshold <- 1 / length(exposures)
  
  weights_df <- wqs_obj$final_weights %>%
    rownames_to_column("pesticide") %>%
    select(pesticide, where(is.numeric)) %>%   # keep only numeric columns
    pivot_longer(
      cols = -pesticide,
      names_to = "model",
      values_to = "weight"
    ) %>%
    mutate(
      model = model_name,
      color_group = ifelse(weight >= threshold, "Above", "Below")
    )
  
  weights_df
}

wqs_all <- bind_rows(
  plot_wqs_weights(WQS.LHemThick, "Left Hemisphere Thickness", Exposure.Names),
  plot_wqs_weights(WQS.RHemThick, "Right Hemisphere Thickness", Exposure.Names),
  plot_wqs_weights(WQS.MeanThick, "Mean Thickness", Exposure.Names),
  plot_wqs_weights(WQS.LHemArea, "Left Hemisphere Area", Exposure.Names),
  plot_wqs_weights(WQS.RHemArea, "Right Hemisphere Area", Exposure.Names),
  plot_wqs_weights(WQS.TotalArea, "Total Area", Exposure.Names)
)

wqs_all <- wqs_all %>%
  mutate(model = factor(model,
                        levels = c(
                          "Left Hemisphere Thickness",  "Left Hemisphere Area",
                          "Right Hemisphere Thickness", "Right Hemisphere Area",
                          "Mean Thickness",
                          "Total Area"
                        )))

wqs_plot <- wqs_all %>%
  group_by(model, pesticide) %>%
  summarise(weight = mean(weight, na.rm = TRUE), .groups = "drop") %>%
  group_by(model) %>%
  mutate(pest_re = reorder_within(pesticide, weight, model)) %>%
  ungroup()

classes <- tibble(
  pesticide = c("DEP","DETP","DMP","DMTP","CINA6","D24","PBA","PNP","TCP","TDCCA"),
  class = c("Organophosphates","Organophosphates","Organophosphates","Organophosphates",
            "Neonicotinoid","Organochlorines","Pyrethroids","Organophosphates",
            "Organochlorines","Pyrethroids")
)

wqs_plot <- wqs_plot %>%
  left_join(classes, by = "pesticide")

class_colors <- c(
 "Organophosphates" = "#4f8f82",   # brighter teal
  "Pyrethroids"      = "#2f74ff",   # brighter blue
  "Neonicotinoid"    = "#f5b800",   # brighter gold-yellow
  "Organochlorines"  = "#c4558a"    # brighter rose-pink
)

p_wqs <- ggplot(wqs_plot, aes(
  x = pest_re,
  y = weight,
  fill = class,
   text = paste0(
    "<b>Pesticide:</b> ", pesticide,
    "<br><b>Class:</b> ", class,
    "<br><b>Weight:</b> ", round(weight, 2),
    "<br><b>Model:</b> ", model
  )
)) +
  geom_bar(stat = "identity") +
  geom_hline(
    yintercept = 1 / length(Exposure.Names),
    linetype = "dashed",
    color = "red"
  ) +
  coord_flip() +
  facet_wrap(~ model, ncol = 2, scales = "free_y") +
  scale_x_reordered() +
  scale_fill_manual(values = class_colors) +
  theme_minimal(base_size = 13) +
  labs(x = NULL, y = "Weight") +
  theme(legend.position = "bottom")  # optional: show class legend

# your recoding (keep exactly as you wrote)
factored <- merged_all %>%
  mutate(
    ethnicity = factor(ethnicity, levels = c(1, 3),
                       labels = c("Black African", "Mixed Ancestry")),
    sex = factor(sex, levels = c(1, 2),
                 labels = c("Female", "Male")),
    maternal_hiv = factor(maternal_hiv, levels = c(0, 1),
                          labels = c("HIV-negative", "HIV-positive")),
    smokecat_anc = factor(smokecat_anc, levels = c(0, 1, 2),
                          labels = c("Non-smoker", "Passive smoker", "Active smoker")),
    education2v = factor(education2v, levels = c(0, 1),
                         labels = c("Lower than secondary",
                                    "At least secondary or higher")),
    household_income = factor(household_income, levels = c(0, 1, 2),
                              labels = c("<R1000/m", "R1000–5000/m", ">R5000/m")),
    parent_work = factor(parent_work, levels = c(0, 1),
                         labels = c("Not working", "Working"))
  )
```

```{r, echo=FALSE, results='asis'}
htmltools::tags$style(HTML("
.big-card {
  background-color: #ffffff;
  border-radius: 10px;
  padding: 20px;
  margin-bottom: 15px;
  text-align: center;
  box-shadow: 0 2px 6px rgba(0,0,0,0.08);
  
  display: flex;                /* flex layout */
  justify-content: center;      /* center horizontally */
  align-items: center;          /* center vertically */
  flex-direction: column;       /* stack number above label */
}
.big-number {
  font-size: 24px;
  font-weight: bold;
}
.big-label {
  font-size: 15px;
  color: #555;
}

"))




```

# Descriptive 

Column {width=650px}
-------------------------------------

```{r, echo=FALSE}
df <- factored

n <- nrow(df)
ethnicity_major <- names(sort(table(df$ethnicity), decreasing=TRUE))[1]
pct_male <- round(mean(df$sex == "Male", na.rm = TRUE)*100)
bw <- round(mean(df$birth_weight, na.rm = TRUE), 0)
#bmi <- round(mean(df$maternal_BMI_anc, na.rm = TRUE), 1)
#hiv <- round(mean(df$maternal_hiv == "HIV-positive", na.rm = TRUE)*100)

HTML(paste0(
  "<div style='display:flex; width:100%; gap:20px; align-items:flex-start;'>",

    
    "<div style='min-width:180px; max-width:200px;'>",
      "<a href='https://github.com/najiyahwilliamson7/Thesis-Dashboard' target='_blank' ",
      "style='font-size:14px; text-decoration:none; color:#4f8f82; font-weight:bold;'>",
      "🔗 GitHub Repository</a>",
    "</div>",

    "<div style='display:flex; gap:15px; flex-wrap:wrap; width:100%;'>",

      "<div class='big-card'><div class='big-number'>", n, "</div><div class='big-label'>Sample Size</div></div>",
      "<div class='big-card'><div class='big-number'>", pct_male, "%</div><div class='big-label'>Male</div></div>",
      "<div class='big-card'><div class='big-number'>", bw, "</div><div class='big-label'>Birth Weight (g)</div></div>",
      "<div class='big-card'><div class='big-number'>", ethnicity_major, "</div><div class='big-label'>Major Ethnicity</div></div>",

    "</div>",

  "</div>"
))

```

```{r, echo=FALSE}
htmltools::tags$style(HTML("
/* Make cards responsive */
@media (max-width: 600px) {
  .big-card {
    width: 100% !important;
    margin: 6px 0 !important;
    padding: 15px !important;
  }
  .big-number {
    font-size: 20px !important;
  }
  .big-label {
    font-size: 13px !important;
  }
}

/* Make plotly widgets scale */
.plotly html-widget {
  width: 100% !important;
  height: auto !important;
}

/* Reduce padding + text sizes on mobile */
@media (max-width: 600px) {
  body {
    padding: 5px !important;
  }
  .section.level3 h3 {
    font-size: 16px !important;
  }
  .navbar {
    font-size: 14px !important;
  }
}
"))
```

```{r, fig.width=8, fig.height=3.7}
# -------------------------
# Pesticides
# -------------------------
merged_all <- read.csv(here("reports/merged_all.csv"))

lod <- read_excel(here("../02_data/pesticides_LOD.xlsx")) %>% 
  clean_names()

# -------------------------
# DEFINE VARIABLES
# -------------------------
pesticide_vars <- c("DEP","DETP","DMP","DMTP","CINA6","D24","PBA","PNP","TCP","TDCCA")

pesticide_raw <- merged_all %>% 
  dplyr::select(all_of(pesticide_vars))

# -------------------------
# METADATA
# -------------------------
classes <- tibble(
  metabolite = pesticide_vars,
  class = c("Organophosphates","Organophosphates","Organophosphates","Organophosphates",
            "Neonicotinoid","Organochlorines","Pyrethroids","Organophosphates",
            "Organochlorines","Pyrethroids")
)

pesticide_names <- tibble(
  metabolite = pesticide_vars,
  name = c("diethyl phosphate (DEP)", "diethyl thiophosphate (DETP)", 
           "dimethyl phosphate (DMP)", "dimethyl thiophosphate (DMTP)",
           "6-nicotinic acid (CINA-6)", "2,4-dichlorophenol (D24)",
           "3-phenoxybenzoic acid (PBA)", "p-nitrophenol (PNP)",
           "2,4,5-trichlorophenol (TCP)", "trans-DCCA (TDCCA)")
)

# -------------------------
# LONG FORMAT + JOIN
# -------------------------
pesticide_long <- pesticide_raw %>%
  pivot_longer(cols = everything(), names_to = "metabolite", values_to = "value") %>%
  left_join(lod, by = "metabolite") %>%
  left_join(classes, by = "metabolite") %>%
  left_join(pesticide_names, by = "metabolite")

# Order classes
class_order <- c("Organophosphates", "Pyrethroids", "Neonicotinoid", "Organochlorines")

pesticide_long <- pesticide_long %>%
  mutate(class = factor(class, levels = class_order))

# -------------------------
# SUMMARY: GEOMETRIC MEAN
# -------------------------
pesticide_plot <- pesticide_long %>%
  group_by(class, name) %>%
  summarise(
    GM = exp(mean(log(ifelse(value < lod, lod / sqrt(2), value)), na.rm = TRUE)),
    .groups = "drop"
  )

# -------------------------
# PLOT
# -------------------------
p_pesticide <- ggplot(pesticide_plot, aes(x = reorder(name, GM), y = GM, fill = class,
    text = paste0(
      "<br><b>Geometric Mean:</b> ", round(GM, 3)
    )
)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  facet_wrap(~ class, ncol = 2, scales = "free_y") +
  theme_minimal(base_size = 11) +
  labs(
    x = NULL,
    y = "Geometric Mean Concentration"
  ) +
  theme(
    strip.text = element_text(face = "bold"),
    axis.text.y = element_text(size = 8)
  ) +
  scale_fill_manual(values = c(
    "Organophosphates" = "#4f8f82",   # brighter teal
  "Pyrethroids"      = "#2f74ff",   # brighter blue
  "Neonicotinoid"    = "#f5b800",   # brighter gold-yellow
  "Organochlorines"  = "#c4558a"    # brighter rose-pink

  ))+ theme(
    plot.margin = margin(5, 20, 5, 5),  # adds right padding
    axis.text.y = element_text(size = 7)
  )

ggplotly(p_pesticide, tooltip = "text") %>% layout(showlegend = FALSE)

```
```{r, echo=FALSE}
div(
  style = "
    clear: both;
    width:100%;
    margin-top:20px;
  ",
  div(
    style = "
      max-width:900px;
      margin-left:auto;
      margin-right:auto;
      background-color:#f7f7f7;
      border-left:4px solid #4f8f82;
      padding:14px 18px;
      font-size:clamp(13px, 1.1vw, 15px);
      line-height:1.5;
    ",
    HTML("
      <b>Why This Matters</b><br><br>
      Prenatal exposure to pesticides may influence early brain development, with potential long-term impacts on cognitive and neurological health. This dashboard provides an accessible way to explore these associations, supporting research and public health efforts aimed at reducing harmful environmental exposures during critical developmental periods.
    ")
  )
)
```



Column {.col-sm-12 .col-md-6}
-------------------------------------

```{r, fig.width=6.3, fig.height=2.3}
thickness_vars <- c(
  "MeanFrontalThickness", "MeanTemporalThickness", "MeanOccipitalThickness",
  "MeanParietalThickness", "MeanCingulateThickness", "MeanInsulaThickness"#,
  # "LeftHemisphereThickness", "RightHemisphereThickness", "MeanThickness"
)

p_thickness <- factored %>%
  summarise(across(all_of(thickness_vars), mean, na.rm = TRUE)) %>%
  pivot_longer(everything(), names_to = "Region", values_to = "Thickness") %>%
  ggplot(aes(x = reorder(Region, Thickness), y = Thickness,
         text = paste0(
      "<b>Region:</b> ", Region,
      "<br><b>Mean Thickness:</b> ", round(Thickness, 3), " mm"
    )
)) +
  geom_col(fill = "#e6c34a") +
  theme_minimal() +
  labs(x = "Region", y = "Cortical Thickness (mm)") +  # vertical bars, show y-axis
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 7),  # rotated x labels
    axis.text.y = element_text(size = 7),
    axis.title.x = element_text(size = 9, face = "bold"),
    axis.title.y = element_text(size = 9, face = "bold")
  )
```

```{r, fig.width=7.3, fig.height=2.3}
area_vars <- c(
  "TotalFrontalArea", "TotalTemporalArea", "TotalOccipitalArea",
  "TotalParietalArea", "TotalCingulateArea", "TotalInsulaArea"#,
  # "LeftHemisphereArea", "RightHemisphereArea", "TotalArea"
)

p_area <- factored %>%
  summarise(across(all_of(area_vars), mean, na.rm = TRUE)) %>%
  pivot_longer(everything(), names_to = "Region", values_to = "Area") %>%
  ggplot(aes(x = reorder(Region, Area), y = Area, ,
    text = paste0(
      "<b>Region:</b> ", Region,
      "<br><b>Mean Surface Area:</b> ", round(Area, 1), " mm²"
    )
)) +
  geom_col(fill = "steelblue") +
  theme_minimal() +
  labs(x = "Region", y = "Cortical Surface Area (mm^2)") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 7),
    axis.text.y = element_text(size = 7),
    axis.title.x = element_text(size = 9, face = "bold"),
    axis.title.y = element_text(size = 9, face = "bold")
  )
```


<!-- ```{r, fig.height=5.5} -->
<!-- p_thickness + p_area + plot_layout(ncol=1) -->
<!-- ``` -->

```{r, fig.width=7.3, fig.height=3.2}
ggplotly(p_thickness, tooltip = "text")
  
```

```{r, fig.width=7.3, fig.height=3.2}
ggplotly(p_area, tooltip = "text")
```



<!-- ### Smoking Status -->

<!-- ```{r, fig.height=4} -->
<!-- factored %>% -->
<!--   count(smokecat_anc) %>% -->
<!--   mutate(p = n / sum(n) * 100) %>% -->
<!--   ggplot(aes(smokecat_anc, p, fill = smokecat_anc)) + -->
<!--   geom_col() + -->
<!--   theme_minimal(base_size = 12) + -->
<!--   theme(legend.position = "none", -->
<!--         axis.text.x = element_text(angle = 30, hjust = 1)) + -->
<!--   labs(x = NULL, y = "Percent") -->
<!-- ``` -->

<!-- ### Mother's Education -->

<!-- ```{r} -->
<!-- factored %>% -->
<!--   count(education2v) %>% -->
<!--   mutate(p = n / sum(n) * 100) %>% -->
<!--   ggplot(aes(education2v, p, fill = education2v)) + -->
<!--   geom_col() + -->
<!--   theme_minimal(base_size = 12) + -->
<!--   theme(legend.position = "none", -->
<!--         axis.text.x = element_text(angle = 30, hjust = 1)) + -->
<!--   labs(x = NULL, y = "Percent") -->
<!-- ``` -->

<!-- ### Household Income -->

<!-- ```{r} -->
<!-- factored %>% -->
<!--   count(household_income) %>% -->
<!--   mutate(p = n / sum(n) * 100) %>% -->
<!--   ggplot(aes(household_income, p, fill = household_income)) + -->
<!--   geom_col() + -->
<!--   theme_minimal(base_size = 12) + -->
<!--   theme(legend.position = "none", -->
<!--         axis.text.x = element_text(angle = 30, hjust = 1)) + -->
<!--   labs(x = NULL, y = "Percent") -->
<!-- ``` -->




# Forest Plots

Row
-----------------------------------------------------------------------

Column {data-width=1000}
-----------------------------------------------------------------------
<div style="
  background-color:#f7f7f7;
  border-left:4px solid #4f8f82;
  padding:12px 18px;
  margin-bottom:15px;
  font-size:clamp(13px, 1.2vw, 16px);
  line-height:1.5;
  max-width:1400px;
">
<b>Linear Regression Models</b><br>
• β estimates adjusted for maternal age, ethnicity, SES, BMI, and ICV<br>
• Red = statistically significant (p < 0.05)<br>
• Points show effect estimates; bars show 95% CI
</div>

Row
-----------------------------------------------------------------------

Column {data-width=1/2}
-----------------------------------------------------------------------

```{r, fig.height=6.5}

ggplotly(p_thick2, tooltip = "text") %>%
  layout(dragmode = "zoom")

```
Column {data-width=1/2}
-----------------------------------------------------------------------

```{r, fig.height=6.5}
ggplotly(p_area2, tooltip = "text")
```




# Weighted Quantile Sum Regression

Row
-----------------------------------------------------------------------

Column {data-width=1000}
-----------------------------------------------------------------------
```{r, echo=FALSE}
div(
  style = "
    background-color:#f7f7f7;
    border-left:4px solid #4f8f82;
    padding:12px 18px;
    margin-bottom:15px;
    font-size:14px;
  ",
  HTML("
    <b>Weighted Quantile Sum (WQS) Regression</b><br>
    • Mixture index constructed using 4 quantiles<br>
    • Weights represent each pesticide’s contribution to the overall mixture effect<br>
    • Red dashed line indicates the expected weight under the null (1/k)<br>
    • Bars are colored by chemical class for interpretability
  ")
)
```

Row
-----------------------------------------------------------------------

Column {data-width=1000}
-----------------------------------------------------------------------
```{r, fig.height=6.5, fig.width=8, out.width="100%"}
ggplotly(p_wqs, tooltip = "text")
```


# Data Description

Row
-----------------------------------------------------------------------

Column {data-width=1000}
-----------------------------------------------------------------------

```{r, echo=FALSE}
div(
  style = "
    max-width:800px;
    margin-left:auto;
    margin-right:auto;
    background-color:#f7f7f7;
    border-left:4px solid #4f8f82;
    padding:16px 20px;
    font-size:clamp(13px, 1.2vw, 16px);
    line-height:1.6;
  ",
  HTML("
    <b>Dataset Overview</b><br><br>
    Data are derived from the Drakenstein Child Health Study (DCHS), a longitudinal birth cohort study conducted in South Africa. The analytic sample includes 120 mother–child pairs with complete data on urinary pesticide metabolites and structural magnetic resonance imaging (MRI) measures. Data were collected between 2012 and 2015, with maternal consent obtained at enrollment and reaffirmed annually. Urinary pesticide metabolites were measured from biobanked samples collected during the second trimester (n=104) and at birth (n=16), and structural MRI data were obtained from a neuroimaging sub-study. The study population consists of pregnant individuals and their children participating in the DCHS cohort.This dataset is not publicly available and is used under restricted access.
  ")
)

